---
title: "wyz.code.testthat"
author: "Fabien GELINEAU"
date: "Last update 2019-08-27"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{wyz.code.testthat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
body {
text-align: justify}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval = TRUE, echo = FALSE}
pkn <- 'wyz.code.testthat'
```


Package **`r pkn`**  aims to generate **testthat** test cases from recorded unit tests.

Read [Offensive programming book](https://neonira.github.io/offensiveProgrammingBook/) to get introduction and advanced knowledge on the topic. 


# Releases 

## 1.1.6

Main improvements are 

1. corrected erroneous write out of tempdir folder
1. completed unit tests
1. enforced higher code coverage (up to 99.40%)
1. clean up package dependencies. 


This release replaces fully olders ones, that are now considered obsoletes. Keep the pace, and 
upgrade your packages if you do not use this version or a higher one!

